---
title: "Homework 3"
author: 'Xinrui Hu (NetID: xh2506)'
output: pdf_document
---

```{r load_packages, include=FALSE}
library(tidyverse)
library(dslabs)
```

**You are required to process the data `us_contagious_diseases` (available from package `dslabs`) via the 5 sequential steps given in the questions below.**

### Question 1 (2 pts): From the data `us_contagious_diseases`, ignoring the variable `weeks_reporting`, compute the yearly incidence rate of each disease for the entire country. Store the result into a new data frame, named as `US_incidence`, with columns `disease`, `year`, and `incidence_per_millon` (i.e., the yearly incidence rate times one million). Provide the output of `head(US_incidence)` and `dim(US_incidence)`. Note that you need to drop the missing values (`NA`) of `us_contagious_diseases` after deleting the variable `weeks_reporting`. 
**Answer:** 
```{r}
data("us_contagious_diseases")
US_incidence <- us_contagious_diseases %>%
  select(-weeks_reporting) %>% 
  drop_na() %>%
  group_by(disease, year) %>%
  summarize(incidence_per_millon = sum(count)/sum(population)*1e6) %>%
  ungroup()
head(US_incidence)
```
```{r}
dim(US_incidence)
```


### Question 2 (2 pts): Pivot the data frame `US_incidence` into a new one that shows the `incidence_per_millon` values for all diseases of the same year at the same row. Still use  the name `US_incidence` for the new data frame. Then provide the output of `head(US_incidence)` and `dim(US_incidence)`. Note that the output of `head(US_incidence)` should look like as follows:
**Answer:** 
```{r}
US_incidence <- US_incidence %>%
  pivot_wider(id_cols = year, names_from = disease, values_from = incidence_per_millon)
head(US_incidence)
```
```{r}
dim(US_incidence)
```



### Question 3 (2 pts): Carefully read the documentation of the function `cor()` of package `stats`. According to the new data frame `US_incidence` from Question 2, compute the Pearson's correlation between `Hepatitis A` and `Measles` in terms of `incidence_per_millon`. Due to missing values, you need to choose an appropriate value for the `use` argument in `cor()`.
**Answer:** 
```{r}
cor(US_incidence$`Hepatitis A`, US_incidence$Measles, use = "pairwise.complete.obs", method = "pearson")
```


### Question 4 (2 pts): According to the new data frame `US_incidence` from Question 2, use one of the `map` functions to compute the Pearson's correlation between `Hepatitis A` and each of the other 6 diseases in terms of `incidence_per_millon`, and return a `double` vector as the output.
**Answer:** 
```{r}
cor_vec <- map_dbl(colnames(US_incidence)[-c(1,2)], ~ cor(US_incidence$'Hepatitis A', US_incidence[, .x], use = "pairwise.complete.obs"), method = "pearson")
rbind(names(US_incidence)[3:8], cor_vec)
```




### Question 5 (2 pts): According to the new data frame `US_incidence` from Question 2, for each of the 7 diseases, find its most positively (Pearson's) correlated disease (except itself) and corresponding correlation. Simplify your code by loops or the `map` functions. 
**Answer:** 
```{r}
library(purrr)
cor_matrix <- cor(US_incidence, use = "pairwise.complete.obs")
diag(cor_matrix) <- NA
most_correlated_disease <- map(colnames(US_incidence), function(disease) {
  disease_cor <- cor_matrix[disease,]
  max_cor_index <- which.max(disease_cor)
  c(colnames(US_incidence)[max_cor_index], disease_cor[max_cor_index])
  })
most_correlated_disease
```

```{r}
df <- US_incidence[,-1]
cor_matrix <- cor(df, use = "pairwise.complete.obs")
cor_matrix
```



