---
title: "In-class Assignment 4"
author: 'Xinrui Hu (NetID: xh2506)'
output: pdf_document
---

```{r, include=FALSE}
library(tidyverse)
```

### Question 1 (1 pt): Use `str_length()` and `str_sub()` to extract the middle character from each string in the vector `x <- c("a", "abc", "abcd", "abcde", "abcdef")`. What will you do if a string has an even number of characters? (Hint: Base R function `floor()` or `ceiling()` may be useful here.)
**Answer:** 
<!--Provide your answer and code below-->
```{r}
x <- c("a", "abc", "abcd", "abcde", "abcdef")
L <- str_length(x)
y <- ceiling(L/2)
str_sub(x,y,y)
```



### Question 2 (1 pt): `words` is a vector with each element being a word, which is available after you run `library(tidyverse)`. From the vector `words`, find the words that have the highest number of vowels?
**Answer:** 
<!--Provide your answer and code below-->
```{r}
vowels <- str_count (words,"[aeiou]")
words[vowels == max(vowels)]
```



### Question 3 (1 pt): `sentences` is a vector with each element being a sentence, which is available after you run `library(tidyverse)`. Extract the first word from each sentence in `sentences`. Use `%>% head(100)` to output the result. 
**Answer:** 
<!--Provide your answer and code below-->
```{r}
str_extract(sentences, boundary("word")) %>% head(100)
```



### Question 4 (1 pt): In the vector `sentences`, find all words that contain an apostrophe. In each found word, separate out the pieces before and after the apostrophe. (Hint: See 14.4.3 Grouped Matches in the textbook.)
**Answer:** 
<!--Provide your answer and code below-->
```{r}
contraction <-"([A-Za-z]*)'([A-Za-z]*)"
sentences %>%
  str_subset(contraction) %>%
  str_match_all(contraction)
```



### Question 5 (1 pt): What are the five most common words in the vector `sentences`? (Hint: You may use `boundary("word")` with an appropriate function. Use the function `unlist()` to convert a list to a vector. The function `count()` may be useful here.)
**Answer:** 
<!--Provide your answer and code below-->
```{r}
tibble(word = str_to_lower(unlist(str_extract_all(sentences, boundary("word"))))) %>%
  count(word, sort = TRUE) %>%
  head(5)
```


