---
title: "In-class Assignment 6"
author: 'Xinrui Hu (NetID: xh2506)'
output: pdf_document
---

```{r, include=FALSE}
library(tidyverse)
```

### Question 1 (1 pt): Write your own function to compute the variance of a numeric vector. Then use your function to compute the variance of `1:100`.
**Answer:** 
```{r}
myfun <- function(x) {
  n <- length(x)
  y <- sum((x-mean(x))^2)/(n-1)
  y
}
myfun(1:100)
```



### Question 2 (1 pt): Write a `fizzbuzz` function. It takes a single number as input. If the number is divisible by three, it returns `"fizz"`. If it’s divisible by five it returns `"buzz"`. If it’s divisible by three and five, it returns `"fizzbuzz"`. Otherwise, it returns the number. Output the results of `fizzbuzz(6)`, `fizzbuzz(10)`, `fizzbuzz(15)` and `fizzbuzz(2)`.
**Answer:** 
```{r}

fizzbuzz <- function(f) {
  if ((f/5) == round(f/5) & (f/3) == round(f/3)){
      "fizzbuzz"
    }else if ((f/5) == round(f/5)){
      "buzz"
    }else if ((f/3) == round(f/3)){
    "fizz"
      }else{
        f}
  }
fizzbuzz(6)
fizzbuzz(10)
fizzbuzz(15)
fizzbuzz(2)
```



### Question 3 (1 pt): Carefully read the documentation of the base R function `cut()`. Modify the following `cold_hot` function by using `cut()` to simplify the set of nested if-else statements. After the modification, output the results of `cold_hot(-5)`, `cold_hot(0)`, `cold_hot(10)`, `cold_hot(20)` and `cold_hot(30)`.
```{r}
cold_hot <- function(temp){
  cut(temp, c(-Inf, 0, 10, 20, 30, Inf),
      right = FALSE,
      labels = c("freezing", "cold", "cool", "warm", "hot"))
}

cold_hot(-5)
cold_hot(0)
cold_hot(10)
cold_hot(20)
cold_hot(30)
```
**Answer:** 



### Question 4 (1 pt): A function called `commas()` is defined below. What does `commas(letters, collapse = "-")` do? Why? (If there is an error when knitting, use the code chunk option `error = TRUE`.)
```{r,error = TRUE}
commas <- function(...) {
  str_c(..., collapse = ", ")
}
commas(letters, collapse = "-")
```
**Answer:** 
```{r}
# Because it add a argument to the function which would gives an error
```



### Question 5 (1 pt): Carefully read the documentation of the function `cor()` of package `stats`. The default value for the `method` argument to `cor()` is `c("pearson", "kendall", "spearman")`. What does that mean? What value is used by default?
**Answer:** 
```{r}
# It means method argument can take one of those three values, the pearson is used by default.
```

